### 2019-10-06 defesa/tex/chapter/e3p.tex
wip

One of the most useful techniques when dealing with complicated functions is approximation. They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined. In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}. For this problem, the approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials.

@@

Chebyshev polynomials are widely used in Numerical Analysis

There are two kinds of very known Chebyshev polynomials. Here, only the first kind will be used, for a more through introduction see \citeonline{chebbook}.

Also known as Chebyshev polynomial of the first kind, $T_n : [-1, 1] \mapsto [-1, 1]$ is defined as follows:

@@

Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives) and it is defined over a closed interval. These two properties provide very nice guarantees about the approximation function that is going to be constructed.

>>>>

One of the most useful techniques when dealing with complicated functions is approximation. They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined. In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}. For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered. The approximation set of functions is going to be the set of $N$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $N$ by $N$ matrix.

@@

Chebyshev polynomials are widely used in Numerical Analysis in areas like numerical integration, polynomial approximation, and ordinary and partial differential equations.
They are also very useful in practice and are present in extension libraries in Python and MATLAB.

Because of the scope of this work, only a brief introduction of Chebyshev polynomials of the first kind and its usage in polynomial interpolation is given. For a more thorough work on the subject, please check the book by \citeonline{chebbook}.

We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind:

@@

Although, its definition can be extended, so its domain is the whole real line, It also respects the following recurrence relation:

\begin{equation}
\begin{array}{ll}
T_0(x) = 1& \\
T_1(x) = x& \\
T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x)&n = 2, 3, \dots
\end{array}
\end{equation}

Even though $\xi(\theta)$ is complicated enough, in a sense that finding its roots directly is no trivial task, it is very well-behaved (it is continuous with infinite continuous derivatives). This property provides very nice guarantees about the approximation function that is going to be constructed.

Polynomial interpolation is a form of approximating a function by a polynomial of degree $N$ that passes through $N+1$ points. In fact, this polynomial is unique and it is determined by Lagrange's formula:

\begin{equation}
\sum_{j=0}^{N} \dfrac{\prod_{k \neq j}^{N+1} (x-x_k)}{\prod_{k \neq j}^{N+1} (x_j-x_k)}.
\end{equation}
